---
title: "ReadMe"
author: Colin Millar
date: 5th November 2016
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 2
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# HEAT assessment tool

## Oxygen Debt Indicator Calculation Scripts

The following as an example of fitting the HEAT oxygen debt profile models to CTD or water bottle data.  The code below assumes that the repository has been cloned and all work is done from the root directory `.../HEAT/`, and that the data has been downloaded and prepared via:

```{r input, echo=TRUE, eval=FALSE}
source("scripts/OxygenDebt/01_input.R")
```

This will create the folder `model` and the file `model/input.csv`.  

```{r example_norun}
# read in data
oxy <- read.csv("model/input.csv")
head(oxy)
```

Now that the data are read in, the following code loads the `oxydebt` package for the `doonefit_full` and `plot_fit` functions.  


```{r example_run, message = FALSE}
# load libraries
library(oxydebt)

# inspect the results from one fit
ID <- 8492
data <- oxy[oxy$ID == ID,]
fit <- doonefit_full(data, ID = ID)

p <- plot_fit(fit, data)
print(p)
```

